|

### 2021-07-27 article/articleCustomerDropoutMembership.Rmd
upd

Table \@ref(tab:summarytable) shows data's summary statistics. 
```{r teste, eval=FALSE, message=FALSE, warning=FALSE, echo=FALSE, paged.print=FALSE}
library(stargazer)
df_summary <- summary(df_members)
stargazer(df_members,
          title = "Summary statistics",
          label = "tab1cars",
          table.placement = "h",
          header = FALSE,
          summary = TRUE,
          summary.stat = c("min", "p25", "median", "p75", "max", "median", "sd")
         )
```
```{r summarytable, eval=TRUE, echo=FALSE, message=FALSE, warning=FALSE}
library(gtsummary)
library(kableExtra)
library(labelled)

@@

as_kable_extra(tbl,booktabs=T,caption="Summary statistics of features used")
```
The average age is `r round(mean(df_members$age,na.rm = TRUE),1)` ±
`r round(sd(df_members$age,na.rm = TRUE),1)`, the members have an attendance 
`r round(mean(df_members$total_matches,na.rm = TRUE),0)` ± `r 
round(sd(df_members$total_matches,na.rm = TRUE),1)` with a membership
`r round(mean(df_members$years_membership,na.rm = TRUE),0)` ± `r 
round(sd(df_members$years_membership,na.rm = TRUE),1)`.
Figure \@ref(fig:membershipyear) shows the distribution of the dropout considering the inscription year.

>>>>

Table \@ref(tab:summarytable) shows data's summary statistics. 
The average age is `r round(mean(df_members$age,na.rm = TRUE),1)` ±
`r round(sd(df_members$age,na.rm = TRUE),1)`, the members have an attendance 
`r round(mean(df_members$total_matches,na.rm = TRUE),0)` ± `r 
round(sd(df_members$total_matches,na.rm = TRUE),1)` with a membership
`r round(mean(df_members$years_membership,na.rm = TRUE),0)` ± `r 
round(sd(df_members$years_membership,na.rm = TRUE),1)`.

```{r teste, eval=FALSE, message=FALSE, warning=FALSE, echo=FALSE, paged.print=FALSE}
library(stargazer)
df_summary <- summary(df_members)
stargazer(df_members,
          title = "Summary statistics",
          label = "tab1cars",
          table.placement = "h",
          header = FALSE,
          summary = TRUE,
          summary.stat = c("min", "p25", "median", "p75", "max", "median", "sd")
         )
```
```{r summarytable, eval=TRUE, echo=FALSE, message=FALSE, warning=FALSE}
library(gtsummary)
library(kableExtra)
library(labelled)

@@

as_kable_extra(tbl,booktabs=T,caption="Summary statistics of features used")
```
Figure \@ref(fig:membershipyear) shows the distribution of the dropout considering the inscription year.
